Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-07-27 limits/ms.tex
pop synth

based on the values and uncertainties from the CMB, but tests using
simulated lenses are desirable.

@@

\subsection{Stellar population synthesis modelling}

For many galaxy lenses, the central potential is dominated by the visible matter. In this situation, constraints on the stellar mass distribution are invaluable. \citep{2008MNRAS.383..857F} demonstrate that with just photometric data in XXX bands, and an assumed initial mass function for the stars, they are able to reliably constrain the stellar mass to XXX\% accuracy. This gives a constraint on the full lensing mass map:

\begin{equation} 
M(\vec\theta) > M_*(\vec\theta)
\end{equation} 
where $M_*$ is the stellar mass (see also similar work by ZZZZZ). Given the above work, we assume from here on that the stellar mass for our mock N-body data can be reliably determined and used as a lower-bound constraint on our lens models.

{\bf JR. Prasenjit: you know more than me about this. Can you fill in the XXX's? We should probably also say a bit more about Ignacio's methodology and why the errors are so good etc etc.}

@@

\item More references to be added to the introduction. Lots of work remains to be cited. Were we really the first to test lensing on N-body mocks? Perhaps for strong lensing, but certainly not for weak.

@@

\item Prasenjit to write/finish section on stellar population synthesis modelling.

>>>>

based on the values and uncertainties from the CMB; tests of this
technique simulated lenses are still awaited, in order to see how far
the results depend on the model assumptions.

@@

\subsection{Stellar populations}

For many galaxy lenses, the gravitational potential in the inner
region is dominated by the stellar mass.  Steller mass can be
estimated by combining photometry and colours with models of the
stellar populations.  Such estimates are reasonably robust, even if
the star-formation history is very uncertain: given a
stellar-population model \citep[such as][]{2003MNRAS.344.1000B} and an
initial mass function (IMF), the stellar mass can be inferred to 0.1
to 0.2 dex using just two photometric bands \citep[see e.g., Figure~1
  in][]{2008MNRAS.383..857F}.  By comparing the lensing-mass and
stellar-mass profiles in elliptical galaxies, it is possible to
extract the radial dependence of the baryonic vs dark-matter fraction
\citep{2005ApJ...623L...5F,2008MNRAS.383..857F,2011ApJ...740...97L}.

The major uncertainty at present in the stellar mass is probably the
IMF.  In the lensing galaxy of the Einstein Cross, the IMF cannot be
much more bottom-heavy than \cite{2003PASP..115..763C}, because
otherwise the stellar mass would exceed the lensing mass
\cite{2010MNRAS.409L..30F}.  More massive galaxies, however, do appear
to have more of their stellar mass in low-mass stars.  This is
indicated by molecular spectral features characteristic of low mass
stars
\citep{2004ApJ...614L.101C,2012ApJ...747...69C,2013MNRAS.429L..15F}.
The \cite{2003PASP..115..763C} would, however, still provide a robust
lower limit on the stellar mass.  Hence, also a limit on the total
mass.  Accordingly, \Glass\ allows a constraint of the form
\begin{equation} 
M(\vec\theta) \geq M_{\rm stel}(\vec\theta)
\end{equation} 
on the total mass.

@@

@@
